---
title: "Example of R/plotly and R/ggplot2"
author: "Timothée Flutre"
date: "23/08/2019"
output:
    html_document:
        toc: true
        toc_float: true
        number_sections: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load the packages

```{r}
if(! suppressPackageStartupMessages(require("plotly")))
  install.packages("plotly")
suppressPackageStartupMessages(library(plotly))
if(! suppressPackageStartupMessages(require("ggplot2")))
  install.packages("ggplot2")
suppressPackageStartupMessages(library(ggplot2))
```

# Example with `plotly`

## Simulate data

```{r}
set.seed(1234)
n <- 100
x <- rnorm(n=n, mean=7, sd=3)
mu <- 13
beta <- 2
epsilon <- rnorm(n=n, mean=0, sd=4)
y <- mu + beta * x + epsilon
```

## Make a classical scatter plot

Non-interactive:
```{r}
plot(x=x, y=y, las=1, main="Simulated data")
```

## Make a `plotly` scatter plot

Interactive:
```{r}
dat <- data.frame(x=x, y=y)
p <- plot_ly(data=dat, x=~x, y=~y, type="scatter", mode="markers")
p
```

Coordinates pop up when hovering a point with the mouse, and any arbitrary text can be added ([example](https://plot.ly/r/text-and-annotations/#adding-informations-to-default-hover-text)).


# Example with `ggplot2` and `plotly`

Sometimes it is very useful to use `ggplot2` as it implements a "grammar of graphics" ([Wickham, 2010](https://doi.org/10.1198/jcgs.2009.07098)).

## Simulate data

```{r}
set.seed(1234)
I <- 3
J <- 10
dat <- data.frame(id=rep(sprintf("ind%02i", 1:J), times=I),
                  a=gl(n=I, k=J, labels=LETTERS[1:I]),
                  y=NA)
for(i in 1:I){
  idx <- which(dat$a == levels(dat$a)[i])
  dat$y[idx] <- rnorm(n=length(idx), mean=0+i, sd=1)
}
str(dat)
```

## Make a classical boxplot

Non-interactive:
```{r}
boxplot(y ~ a, data=dat, las=1, main="Simulated data")
```

## Make a `plotly` violin plot

Interactive:
```{r}
p <- plot_ly(data=dat, x=~a, y=~y, split=~a, type="violin")
p
```

## Make a `ggplot2` plot

```{r}
p <- ggplot(dat, aes(x=a, y=y, color=a)) +
  labs(title="Simulated data")
p <- p + geom_jitter(position=position_jitter(0.05))
p
```

## Make a `ggplot2 + plotly` plot

Add a `text` argument to `aes`; it will be safely ignored by `ggplot` but used by `plotly`:
```{r}
p <- ggplot(dat, aes(x=a, y=y, color=a,
                     text=id)) +
  labs(title="Simulated data")
p <- p + geom_jitter(position=position_jitter(0.05))
ggplotly(p, tooltip="text")
```
