---
title: "Project \"light\""
author: "authors (individual or team names)"
date: "`r format(Sys.time(), '%d/%m/%Y %H:%M:%S')`"
lang: "en"
colorlinks: true
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: TRUE
    code_folding: show
  pdf_document:
    toc: true
    toc_depth: 3
    number_sections: TRUE
urlcolor: blue
abstract: |
    This document is part of [project "light"](https://github.com/timflutre/tuto-reproducible-research). This project is part of a presentation which teaches the fundamentals of reproducible research, using the free software [R](http://www.r-project.org/).
---

<!--
This R chunk is used to set up some options.
-->
```{r setup, include=FALSE}
suppressPackageStartupMessages(library(knitr))
## retrieve the parameters passed via `rmarkdown::render()`
## (especially handy when used with my own script `rmd2out.R`)
## and rename them into `paramsKnitr` to avoid name conflicts
if(! "paramsKnitr" %in% ls()){
  if("params" %in% ls()){
    paramsKnitr <- params
    rm(params)
  } else
    paramsKnitr <- list(root.dir=NULL)
}
opts_chunk$set(echo=TRUE, warning=TRUE, message=TRUE, cache=FALSE,
               fig.align="center", root.dir=paramsKnitr$root.dir)
opts_knit$set(progress=TRUE, verbose=TRUE)
```


# Preamble

This document was generated from a text file in the Rmd format, especially useful with the free software [R](http://www.r-project.org/) (use a recent-enough version).

For an Rmd file to be successfully exported to HTML and PDF, read [this page](http://rmarkdown.rstudio.com/).

Concretely, open R and type:
```{r ex_rmd, eval=FALSE}
library(rmarkdown)
render("file.Rmd", "all")
```

Any Rmd file is best edited with [RStudio](http://www.rstudio.com/), or [Emacs](http://www.gnu.org/software/emacs/) with [ESS](http://ess.r-project.org/), [markdown](http://jblevins.org/projects/markdown-mode/) and [polymode](https://github.com/vitoshka/polymode).

Example of an equation written in [LaTeX](http://www.latex-project.org/) (free, online [book](https://en.wikibooks.org/wiki/LaTeX)): $y_i \sim \mathcal{N}(\mu, \sigma^2)$

Example of an unordered list:

* $\mu$

* $\sigma$

Example of an ordered list:

1. $\mu$

2. $\sigma$

Example of **bold** and *italics*.

Example of a plot from R (setting the seed for reproducibility):
```{r plot_hist}
set.seed(1859)
hist(rnorm(10^4), breaks="FD")
```

Example of a table from R:
```{r show_table, results='asis'}
knitr::kable(mtcars[1:5,])
```


# Overview

This document is part of the ["light"](https://github.com/timflutre/tuto-reproducible-research) project.
This project is part of a presentation which teaches the fundamentals of reproducible research.

The project directory is organized as advised by Noble [(PLoS Computational Biology, 2009)](http://dx.doi.org/10.1371/journal.pcbi.1000424).

On any Unix-like system, it is easily done with the following commands:
```{r create_proj, eval=FALSE}
touch AUTHORS COPYING README; mkdir -p doc data src results
```

On any Unix-like system, it can also be easily compressed and transferred:
```{r archive_proj, eval=FALSE}
cd ..; tar -czvf project-light.tar.gz \
--exclude="*~" --exclude=".*" project-light
```

Paths:
```{r, eval=FALSE}
projectName <- "project-light"
projectDir <- ""
if(Sys.info()["user"] == "tflutre"){
  projectDir <- file.path("~/src/tuto-reproducible-research",
                           projectName)
} else if(Sys.info()["user"] == "<collaborator1>"){
  projectDir <- file.path("C:/Documents/tuto-reproducible-research",
                           projectName)
}
projectDir <- path.expand(projectDir)
stopifnot(dir.exists(projectDir))
dataDir <- file.path(projectDir, "data")
stopifnot(dir.exists(dataDir))
results.dir <- file.path(projectDir, "results")
stopifnot(dir.exists(results.dir))
srcDir <- file.path(projectDir, "src")
stopifnot(dir.exists(srcDir))
## source(file.path(srcDir, paste0(projectName, "_utils.R")))
```

Dependencies:
```{r, eval=FALSE}
suppressPackageStartupMessages(library(MASS))
```

Execution time (see the appendix):
```{r time_0}
t0 <- proc.time()
```


# Load (or simulate) some data

Before loading a file, it is useful to check that its content did not change using the [MD5](https://en.wikipedia.org/wiki/MD5) digest algorithm:
```{r, eval=FALSE}
inF <- file.path(dataDir, "data.tsv")
stopifnot(tools::md5sum(inF) == "baaf3c3eb892c5e4c42327eee462b35e") # fake example
dat <- read.table(inF, header=TRUE, sep="\t")
```


# Explore the data

Use `plot()`, `hist()`, `boxplot()` (better, `beanplot()`), `barplot`, etc, or `ggplot2` and `plotly`.

...


# Write the model

Use [LaTeX](https://en.wikibooks.org/wiki/LaTeX) syntax.

...


# Perform inference

Use `lm()`, `lme4::lmer()`, etc.

...


# Check assumptions

Look at residuals, etc.

...


# Appendix

```{r info}
t1 <- proc.time(); t1 - t0
print(sessionInfo(), locale=FALSE)
```
