---
title: "Project \"light\""
author: "authors (individual or team names)"
date: "`r format(Sys.time(), '%d/%m/%Y %H:%M:%S')`"
colorlinks: true
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: TRUE
  pdf_document:
    toc: true
    toc_depth: 3
    number_sections: TRUE
urlcolor: blue
---

<!--
This R chunk is used to set up some options.
-->
```{r setup, include=FALSE}
R.v.maj <- as.numeric(R.version$major)
R.v.min.1 <- as.numeric(strsplit(R.version$minor, "\\.")[[1]][1])
if(R.v.maj < 2 || (R.v.maj == 2 && R.v.min.1 < 15))
  stop("requires R >= 2.15", call.=FALSE)

suppressPackageStartupMessages(library(knitr))
opts_chunk$set(echo=TRUE, warning=TRUE, message=TRUE, cache=FALSE, fig.align="center")
```


# Preamble

This document was generated from a text file in the Rmd format, especially useful with the free software [R](http://www.r-project.org/) (use a recent-enough version).

For an Rmd file to be successfully exported to HTML and PDF, read [this page](http://rmarkdown.rstudio.com/).

Concretely, open R and type:
```{r ex_rmd, eval=FALSE}
library(rmarkdown)
render("file.Rmd", "all")
```

Any Rmd file is best edited with [RStudio](http://www.rstudio.com/), or [Emacs](http://www.gnu.org/software/emacs/) with [ESS](http://ess.r-project.org/), [markdown](http://jblevins.org/projects/markdown-mode/) and [polymode](https://github.com/vitoshka/polymode).

Example of an equation written in [LaTeX](http://www.latex-project.org/) (free, online [book](https://en.wikibooks.org/wiki/LaTeX)): $y_i \sim \mathcal{N}(\mu, \sigma^2)$

Example of an unordered list:

* $\mu$

* $\sigma$

Example of an ordered list:

1. $\mu$

2. $\sigma$

Example of **bold** and *italics*.

Example of a plot from R (setting the seed for reproducibility):
```{r plot_hist}
set.seed(1859)
hist(rnorm(10^4), breaks="FD")
```

Example of a table from R:
```{r show_table, results='asis'}
knitr::kable(mtcars[1:5,])
```


# Overview

This document is part of [project "light"](https://github.com/timflutre/tuto-reproducible-research).
This project is part of a presentation which teaches the fundamentals of reproducible research.

The project directory is organized as advised by Noble [(PLoS Computational Biology, 2009)](http://dx.doi.org/10.1371/journal.pcbi.1000424).

On any Unix-like system, it is easily done with the following commands:
```{r create_proj, eval=FALSE}
touch AUTHORS COPYING README; mkdir -p doc data src results
```

On any Unix-like system, it can also be easily compressed and transferred:
```{r archive_proj, eval=FALSE}
cd ..; tar -czvf project-light.tar.gz \
--exclude="*~" --exclude=".*" project-light
```

This project involves the following persons:

* Firstname Lastname (specify contributions following R [guidelines](http://journal.r-project.org/archive/2012-1/RJournal_2012-1_Hornik~et~al.pdf))

* ...

Importantly, before anything else, one must specify all paths relatively to the root of the project:
```{r project_organization, eval=FALSE}
project.name <- "project-light"
project.dir <- ""
if(Sys.info()["user"] == "tflutre"){
  project.dir <- "~/src/tuto-reproducible-research/project-light"
} else if(Sys.info()["user"] == "<collaborator1>"){
  project.dir <- "C:/Documents/tuto-reproducible-research/project-light"
}
stopifnot(file.exists(project.dir))
data.dir <- paste0(project.dir, "/data")
stopifnot(file.exists(data.dir))
src.dir <- paste0(project.dir, "/src")
stopifnot(file.exists(src.dir))
## source(paste0(src.dir, "/utils_project-light.R"))
```

This document will also require external packages to be available, for instance:
```{r load_pkg}
## suppressPackageStartupMessages(library(MASS))
```

This R chunk is used to assess how much time it takes to execute the R code in this document until the end:
```{r time_0}
t0 <- proc.time()
```


# Load (or simulate) some data

...


# Explore the data

...


# Write the model

...


# Perform inference

...


# Check assumptions and improve the model

...


# Appendix

```{r info}
t1 <- proc.time(); t1 - t0
print(sessionInfo(), locale=FALSE)
```
